Stats

### 2022-04-08 stats/analysis.Rmd
review ext vali section

n_distinct(extvali$subjID)
```

@@

```{r extvali_plot}
extvaliPostSamples <- bind_rows(
  posterior_samples(mExtvaliccAge, pars = "b_ccAge") %>% mutate(model = "mExtvaliccAge") %>% rename(estimate = b_ccAge), 
  posterior_samples(mExtvaliccHours, pars = "b_ccHours") %>% mutate(model = "mExtvaliccHours") %>% rename(estimate = b_ccHours), 
  posterior_samples(mExtvalihhTotal, pars = "b_hhTotal") %>% mutate(model = "mExtvalihhTotal") %>% rename(estimate = b_hhTotal), 
  posterior_samples(mExtvalihhSibs, pars = "b_hhSibs") %>% mutate(model = "mExtvalihhSibs") %>% rename(estimate = b_hhSibs),
  posterior_samples(mExtvalisibsChildAged, pars = "b_sibsChildAged") %>% mutate(model = "mExtvalisibsChildAged") %>% rename(estimate = b_sibsChildAged),
  posterior_samples(mExtvalisiblingsVarietyScoreP, pars = "b_siblingsVarietyScoreP") %>% mutate(model = "mExtvalisiblingsVarietyScoreP") %>% rename(estimate = b_siblingsVarietyScoreP),
  posterior_samples(mExtvalisiblingsVarietyScoreW, pars = "b_siblingsVarietyScoreW") %>% mutate(model = "mExtvalisiblingsVarietyScoreW") %>% rename(estimate = b_siblingsVarietyScoreW),
  posterior_samples(mExtvaliPE, pars = "b_pe") %>% mutate(model = "mExtvaliPE") %>% rename(estimate = b_pe)
) %>% 
  mutate(
    model = factor(model, levels = extvaliModelorder) %>% str_remove(., "mExtvali"), 
  )

write.csv(extvali_results, "../saves/extvali-posteriorsamples.csv", quote = F, row.names = F)
saveRDS(extvali_results, "../saves/extvali-posteriorsamples.rds")

ggplot(extvaliPostSamples, aes(x = estimate, y = model, fill = factor(stat(quantile)))) +
  geom_vline(xintercept = 0, lty = 2, alpha = .75) +
  stat_density_ridges(
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE, 
    quantiles = c(0.025, 0.975)
  ) +	
  scale_fill_manual(values = c("#006c66", "NA", "#006c66"), guide = "none")

ggsave("../figures/extvali-posteriorsample.png")
```

>>>>

n_distinct(mDataExtvali$subjID)
```

@@

```{r extvali_savemodels}
write.csv(mExtvalinull, "../saves/extvali-mExtvalinull.csv", quote = F, row.names = F)
saveRDS(mExtvalinull, "../saves/extvali-mExtvalinull.rds")

write.csv(mExtvaliccAge, "../saves/extvali-mExtvaliccAge.csv", quote = F, row.names = F)
saveRDS(mExtvaliccAge, "../saves/extvali-mExtvaliccAge.rds")

write.csv(mExtvaliccHours, "../saves/extvali-mExtvaliccHours.csv", quote = F, row.names = F)
saveRDS(mExtvaliccHours, "../saves/extvali-mExtvaliccHours.rds")

write.csv(mExtvalihhTotal, "../saves/extvali-mExtvalihhTotal.csv", quote = F, row.names = F)
saveRDS(mExtvalihhTotal, "../saves/extvali-mExtvalihhTotal.rds")

write.csv(mExtvalihhSibs, "../saves/extvali-mExtvalihhSibs.csv", quote = F, row.names = F)
saveRDS(mExtvalihhSibs, "../saves/extvali-mExtvalihhSibs.rds")

write.csv(mExtvalisibsChildAged, "../saves/extvali-mExtvalisibsChildAged.csv", quote = F, row.names = F)
saveRDS(mExtvalisibsChildAged, "../saves/extvali-mExtvalisibsChildAged.rds")

write.csv(mExtvalisiblingsVarietyScoreP, "../saves/extvali-mExtvalisiblingsVarietyScoreP.csv", quote = F, row.names = F)
saveRDS(mExtvalisiblingsVarietyScoreP, "../saves/extvali-mExtvalisiblingsVarietyScoreP.rds")

write.csv(mExtvalisiblingsVarietyScoreW, "../saves/extvali-mExtvalisiblingsVarietyScoreW.csv", quote = F, row.names = F)
saveRDS(mExtvalisiblingsVarietyScoreW, "../saves/extvali-mExtvalisiblingsVarietyScoreW.rds")

write.csv(mExtvaliPE, "../saves/extvali-mExtvaliPE.csv", quote = F, row.names = F)
saveRDS(mExtvaliPE, "../saves/extvali-mExtvaliPE.rds")
```

```{r extvali_plot}
extvaliPostSamples <- bind_rows(
  posterior_samples(mExtvaliccAge, pars = "b_ccAge") %>% mutate(model = "mExtvaliccAge") %>% rename(estimate = b_ccAge), 
  posterior_samples(mExtvaliccHours, pars = "b_ccHours") %>% mutate(model = "mExtvaliccHours") %>% rename(estimate = b_ccHours), 
  posterior_samples(mExtvalihhTotal, pars = "b_hhTotal") %>% mutate(model = "mExtvalihhTotal") %>% rename(estimate = b_hhTotal), 
  posterior_samples(mExtvalihhSibs, pars = "b_hhSibs") %>% mutate(model = "mExtvalihhSibs") %>% rename(estimate = b_hhSibs),
  posterior_samples(mExtvalisibsChildAged, pars = "b_sibsChildAged") %>% mutate(model = "mExtvalisibsChildAged") %>% rename(estimate = b_sibsChildAged),
  posterior_samples(mExtvalisiblingsVarietyScoreP, pars = "b_siblingsVarietyScoreP") %>% mutate(model = "mExtvalisiblingsVarietyScoreP") %>% rename(estimate = b_siblingsVarietyScoreP),
  posterior_samples(mExtvalisiblingsVarietyScoreW, pars = "b_siblingsVarietyScoreW") %>% mutate(model = "mExtvalisiblingsVarietyScoreW") %>% rename(estimate = b_siblingsVarietyScoreW),
  posterior_samples(mExtvaliPE, pars = "b_pe") %>% mutate(model = "mExtvaliPE") %>% rename(estimate = b_pe)
) %>% 
  mutate(
    model = factor(model, levels = extvaliModelorder, labels = c("sibling variety score (Cassidy et al., 2005)", "number of children in household aged 1-12", "number of children in household aged 0-18", "null model", "number of household members", "average hours spent in childcare per day", "age of childcare entry", "sibling variety score (Peterson, 2000)", "peer exposure index"))  
  )

write.csv(extvaliPostSamples, "../saves/extvali-posteriorsamples.csv", quote = F, row.names = F)
saveRDS(extvaliPostSamples, "../saves/extvali-posteriorsamples.rds")

ggplot(extvaliPostSamples, aes(x = estimate, y = model, fill = factor(stat(quantile)))) +
  geom_vline(xintercept = 0, lty = 2, alpha = .75) +
  stat_density_ridges(
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE, 
    quantiles = c(0.025, 0.975)
  ) +	
  scale_fill_manual(values = c("firebrick", "NA", "firebrick"), guide = "none") + 
  scale_x_continuous(limits = c(-0.25, 0.75)) + 
  ylab("")

ggsave("../figures/extvali-posteriorsample.png", width = 6, height = 3)
```
